Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches

### 2018-01-31 paper/paper.Rmd
ackowledgement language
added keywords

authors: 
- name: Stephanie Kobakian
  thanks: The authors gratefully acknowledge Tennis Australia.
  affiliation: Monash University

@@

keywords:
- data science
- sports analytics
- shiny
- R

>>>>

authors: 
- name: Stephanie Kobakian
  thanks: The authors gratefully acknowledge Tennis Australia providing data for this project.
  affiliation: Monash University

@@

keywords:
- data science
- sports analytics
- shiny
- R
- statistics
- glm
- data visualization
